Opening up the court (surface) in tennis grand slams

### 2020-09-20 paper_results/EDA/graphics_eda.Rmd
change spaniards to spanish players

```{r, fig.height=6, fig.width=16, fig.align='center'}
p1 <- ggplot(spain_wins, aes(round, win_prop, color=tournament, group=tournament)) + 
  labs(title = "Win proportion among Spaniards",
       x = "", y = "Win proportion") + 
    geom_line(size=3) + 
  scale_color_manual(guide=FALSE, values=tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)",
                                           "French Open\n(Clay)",
                                           "US Open\n(DecoTurf)",
                                           "Wimbledon\n(Grass)")) + my_theme

p2 <- ggplot(spain_wins, aes(round, avg_ranking, color=tournament, group=tournament, fill = tournament)) + 
  geom_line(size=3) + 
  labs(title = "Average ranking among Spaniards",
       x = " ",
       y = "Average rank") + 
  scale_color_manual(" ", values=tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)",
                                           "French Open\n(Clay)",
                                           "US Open\n(DecoTurf)",
                                           "Wimbledon\n(Grass)")) + my_theme +
  guides(color = guide_legend(override.aes = list(size = 7)))

@@

ggplot(spain_wins, aes(round, med_ranking, color=tournament, group=tournament, fill = tournament)) + 
  geom_line(size=3) + 
  labs(title = "Median ranking among Spaniards",
       x = " ",
       y = "Median rank") + 
  scale_color_manual(" ", values=tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)",
                                           "French Open\n(Clay)",
                                           "US Open\n(DecoTurf)",
                                           "Wimbledon\n(Grass)")) + my_theme +
  guides(color = guide_legend(override.aes = list(size = 7)))

@@

if(save_graph){
ggsave("../plots/errors_aces2_v2.jpg", height = 6, width = graphic_width_short)
}
```

>>>>

```{r, fig.height=6, fig.width=16, fig.align='center'}
p1 <- ggplot(spain_wins, aes(round, win_prop, color=tournament, group=tournament)) + 
  labs(title = "Spanish Player Performance",
       x = "", y = "Win proportion") + 
    geom_line(size=3) + 
  scale_color_manual(guide=FALSE, values=tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)",
                                           "French Open\n(Clay)",
                                           "US Open\n(DecoTurf)",
                                           "Wimbledon\n(Grass)")) + my_theme

p2 <- ggplot(spain_wins, aes(round, avg_ranking, color=tournament, group=tournament, fill = tournament)) + 
  geom_line(size=3) + 
  labs(title = "Ranking of Spanish Players",
       x = " ",
       y = "Average rank") + 
  scale_color_manual(" ", values=tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)",
                                           "French Open\n(Clay)",
                                           "US Open\n(DecoTurf)",
                                           "Wimbledon\n(Grass)")) + my_theme +
  guides(color = guide_legend(override.aes = list(size = 7)))

@@

p2 <- ggplot(spain_wins, aes(round, med_ranking, color=tournament, group=tournament, fill = tournament)) + 
  geom_line(size=3) + 
  labs(title = "Spanish Player Rankings",
       x = " ",
       y = "Median rank") + 
  scale_color_manual(" ", values=tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)",
                                           "French Open\n(Clay)",
                                           "US Open\n(DecoTurf)",
                                           "Wimbledon\n(Grass)")) + my_theme +
  guides(color = guide_legend(override.aes = list(size = 7)))

if(save_graph){
ggarrange( p1, p2, nrow=1, ncol=2, common.legend = TRUE, legend="bottom") %>%
  ggsave("../plots/spainards_v2_med.jpg", ., height=6, width=graphic_width_long)
}

@@

if(save_graph){
ggsave("../plots/errors_aces2_v2.jpg", height = 6, width = graphic_width_short)
}

which((gs_partial_v2$w_n_ue + gs_partial_v2$l_n_ue)/(gs_partial_v2$w_pointswon + gs_partial_v2$l_pointswon) > 1)

gs_partial_v2[-c(1181), ] %>% 
ggplot(aes((w_n_ue + l_n_ue)/(w_pointswon + l_pointswon),
                          (w_n_aces + l_n_aces)/(w_pointswon + l_pointswon),
                           label = tournament, color=tournament)) + 
  geom_jitter(size=1.8) + # used to be size=2 in v1
  labs( title = "Distribution of errors and aces by slam",
        x = "UE% = unforced errors / total points", y = "ace% = aces / total points") +
  my_theme + scale_color_manual(" ",
                                values = tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)\n",
                                           "French Open\n(Clay)\n",
                                           "US Open\n(DecoTurf)\n",
                                           "Wimbledon\n(Grass)\n")) +
  stat_ellipse(type="t", size = 2) +
  guides(color = guide_legend(override.aes = list(size = 7, shape=15)))

if(save_graph){
ggsave("../plots/errors_aces2_v2_perc.jpg", height = 6, width = graphic_width_short)
}
```
